Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-03 p2/rec-sound.tex
Various improvements
Updated script
Minor improvements

\begin{myth}\mlabel{reconciliation_correct}
If $A$ and $B$ are simple, then $\worksmbx{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{myth}

@@

\begin{proof}
We prove that
if all commands are marked in $A$ that also appear in $B$,
then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.

@@

Let us consider therefore the marked command preceded by an unmarked command in $A$,
and let the marked command be $\cxynv$, 
and the preceding unmarked command be $\czwmv$:
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots
\end{gather*}
As $A$ is simple and $\wrks{A}$, from 
\cref{ax_distantrel_breaks,simple_distant_pairs}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $A$,
and we show that the last two cases are impossible as they would lead to contradiction.

@@

\bigskip

\noindent
We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
to the beginning of $A$ and $B$, and so this is equivalent to
\[ \worksmbx{\acb\cc\amb, \acb\cc\bma}{\acb\cc \bma\cc \reca}. \]

For ease of reading, let us rename
\begin{itemize}
\item $\amb$ to $S$
\item $\reca$ to $S^*$
\item $\bma$ to $T$
\item and $\acb$ to $U$.
\end{itemize}
In this notation, we intend to prove that
\[ \worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}. \]
We can do so if we can show that
\[ \worksmbx{S,T}{S^*}. \]

@@

\bigskip

\noindent
To restate some results above, we therefore already know the following:
\begin{itemize}
\item $S=\amb$ and $T=\bma$ are simple as $A$ and $B$ are simple
\item $S\cap T = \amb \cap \bma = \emptyset$
\item 
$S^*$ is the largest subset of $S$ for which $S^*\indep T$, as
$\reca$ is the largest subset of $\amb$ for which $\reca\indep\bma$
\end{itemize}

Our theorem is therefore proven if we prove the following lemma.
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\begin{mylem}\mlabel{reconciliation_correct_part}
If
{\condSimple} $S$ and $T$ are simple sequences,
{\condDisj} $S\cap T=\emptyset$,
and {\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
then
$\worksmbx{S,T}{S^*}$.
\end{mylem}

>>>>

\begin{myth}\mlabel{reconciliation_correct}
If $A$ and $B$ are simple, then $\worksmbx{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \mbox{~and~}  \alpha\indep \bmanp }. \]
\end{myth}

@@

\begin{proof}
Mark those commands in $A$ that are also in $B$.
We show that
there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.

@@

Let us consider therefore the marked command preceded by an unmarked command in $A$,
and let the marked command be $\cxynv$, 
and the preceding unmarked command be $\czwmv$:
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots
\end{gather*}
As $A$ is simple and $\wrks{A}$, from 
\cref{ax_distantrel_breaks,simple_distant_pairs}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $A$,
and we show that the last two cases are impossible.

@@

We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
to the beginning of $A$ and $B$, and so this is equivalent to
\[ \worksm{\big\{\acb\cc\amb,~ \acb\cc\bma\big\}}{\acb\cc \bma\cc \reca}. \]

For ease of reading, let us rename
\begin{itemize}
\item $\amb$ to $S$,
\item $\reca$ to $S^*$,
\item $\bma$ to $T$,
\item and $\acb$ to $U$.
\end{itemize}
In this notation, we intend to prove that
\[ \worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}. \]
We can do so if we can show that
\[ \worksmbx{S,T}{S^*}. \]

@@

To restate some results above, we therefore already know the following:
\begin{itemize}
\item $S=\amb$ and $T=\bma$ are simple as $A$ and $B$ are simple
\item $S\cap T = \amb \cap \bma = \emptyset$
\item $S^*$ is the largest subset of $S$ for which $S^*\indep T$, as
$\reca$ is the largest subset of $\amb$ for which $\reca\indep\bma$.
\end{itemize}
Our theorem is therefore proven if we prove the following lemma.
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\begin{mylem}\mlabel{reconciliation_correct_part}
If
{\condSimple} $S$ and $T$ are simple sequences,
{\condDisj} $S\cap T=\emptyset$,
and {\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
then
$\worksmbx{S,T}{S^*}$.
\end{mylem}
